Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-19 paper/ijcai/paper.tex
more fixes

\begin{abstract}
Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis.  Dynamic Slicing (\ds{}) and
Spectrum-based Fault Localization (\sfl{}) are very popular fault diagnosis
techniques and normally seen as complementary.  This paper reports the outcome
of a study using real-world applications with the goal of demystifying the
impact of combining \ds{} with \sfl{}.  We suspect that several highly
suspicious components---often involved in failing, but seldom in passing
executions---may be unrelated to the bug. With the aforementioned combination,
such components could be identified and their suspiciousness reduced.  This
study also discusses the impact of the dynamic slicing key limitation---the risk
of missing faulty statements. Our results show that, in practice, \ds{} rarely
misses faulty statements (\Fix{X} misses in \Fix{Y} cases) and that the
\ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
in \Rui{x\% on average}. To sum, we found that, despite tacit opinions of the
research community about the usefulness of \ds{} in automated debugging, we
found the combination practical and effective, and encourage new \sfl{}
techniques to be evaluated against that optimization.
\end{abstract}

@@

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576}
as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
a technique that traces back statements in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{} \Rui{DS, not introduced at this point
in the intro}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available at \textit{$<$anonymized for double-blind review$>$}.

@@

		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}         &  54 & 84.4\%  & 54  & 84.4\%
		 				& 64 & 100\% & 62 & 96.9\% & 64      \\
		\cmath{}           & 82 & 81.2\%  & 86 & 85.1\%
						& 90 & 89.1\% & 97 & 96.0\% & 101  \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Rui{explain what $k$ is for SFL alone.}}
  \label{table:fsws}
\end{table*}

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis.  Dynamic Slicing (\ds{}) and
Spectrum-based Fault Localization (\sfl{}) are very popular fault diagnosis
techniques and normally seen as complementary.  This paper reports the outcome
of a study using real-world applications with the goal of demystifying the
impact of combining \ds{} with \sfl{}.  We suspect that several highly
suspicious components---often involved in failing, but seldom in passing
executions---may be unrelated to the bug. With the aforementioned combination,
such components could be identified and their suspiciousness reduced.  This
study also discusses the impact of the dynamic slicing key limitation---the risk
of missing faulty statements. Our results show that, in practice, \ds{} rarely
misses faulty statements (22 misses in 256 cases) and that the
\ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
in \Rui{x\% on average}. To sum, we found that, despite tacit opinions of the
research community about the usefulness of \ds{} in automated debugging, we
found the combination practical and effective, and encourage new \sfl{}
techniques to be evaluated against that optimization.
\end{abstract}

@@

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576}
as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
a technique that traces back statements in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available at \textit{$<$anonymized for double-blind review$>$}.

@@

		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}         &  54 & 84.4\%  & 54  & 84.4\%
		 				& 64 & 100\% & 62 & 96.9\% & 64      \\
		\cmath{}           & 82 & 81.2\%  & 86 & 85.1\%
						& 90 & 89.1\% & 97 & 96.0\% & 101  \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
	 Total      & 203  &  & 213 & 
	 				& 223 &  & 234 &  & 256 \\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Rui{explain what $k$ is for SFL alone.}}
  \label{table:fsws}
\end{table*}
